---
title: "Hw10Answer"
output: pdf_document
---

```{r}
############################################################
# Homework
# Chapter 6 - Linear Model Selection and Regularization
############################################################

knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ISLR)
library(MASS)
library(leaps)
library(glmnet)

############################################################
# 1) Predict per capita crime rate in the Boston data set
############################################################

data(Boston)
names(Boston)
dim(Boston)
head(Boston)
?Boston
set.seed(2026)

train <- sample(1:nrow(Boston), nrow(Boston)/2)
test <- (-train)

Boston.train <- Boston[train, ]
Boston.test <- Boston[test]

############################################################
# Best subset selection
############################################################

regfit <- regsubsets(crim ~ ., data = Boston.train, nvmax = 13)
reg_summary <- summary(regfit)

names(reg_summary)

reg_summary$cp
reg_summary$bic
reg_summary$adjr2

which.min(reg_summary$cp)
which.min(reg_summary$bic)
which.max(reg_summary$adjr2)

coef(regfit, which.min(reg_summary$cp))
coef(regfit, which.min(reg_summary$bic))
coef(regfit, which.max(reg_summary$adjr2))
```

```{r}
data <- data.frame(adjR2 = reg_summary$adjr2, numVar = seq(1,13))

ggplot(data, aes(y = adjR2, x = numVar)) + 
  geom_point(color = "Red") + 
  geom_line() + 
  theme_bw() +
  scale_x_continuous(breaks = c(1:13), name = "Number of variables")
```

```{r}
data <- data.frame(CP = reg_summary$cp, numVar = seq(1,13))

ggplot(data, aes(y = CP, x = numVar)) + 
  geom_point(color = "Blue") + 
  geom_line() + 
  theme_bw() +
  scale_x_continuous(breaks = c(1:13), name = "Number of variables")
```

```{r}
data <- data.frame(BIC = reg_summary$bic, numVar = seq(1,13))

ggplot(data, aes(y = BIC, x = numVar)) + 
  geom_point(color = "Dark Green") + 
  geom_line() + 
  theme_bw() +
  scale_x_continuous(breaks = c(1:13), name = "Number of variables")
```

```{r}
## Forward Stepwise Selection
regfit_fwd <- regsubsets(crim ~ ., data = Boston.train,
                         nvmax = 13, method = "forward")

fwd_summary <- summary(regfit_fwd)
fwd_summary 
which.min(fwd_summary$cp)
which.min(fwd_summary$bic)

coef(regfit_fwd, which.min(fwd_summary$cp))
coef(regfit_fwd, which.min(fwd_summary$bic))
```

```{r}
## Backward Elemination
regfit_bwd <- regsubsets(crim ~ ., data = Boston.train,
                         nvmax = 13, method = "backward")

bwd_summary <- summary(regfit_bwd)

which.min(bwd_summary$cp)
which.min(bwd_summary$bic)

coef(regfit_bwd, which.min(bwd_summary$cp))
coef(regfit_bwd, which.min(bwd_summary$bic))
```

```{r}
#Ridge Regression 
library(MASS)
library(glmnet)

data(Boston)

set.seed(1)

train <- sample(1:nrow(Boston), nrow(Boston)/2)
test <- (-train)

x <- model.matrix(crim ~ ., Boston)[, -1]
y <- Boston$crim

x.train <- x[train, ]
x.test  <- x[test, ]
y.train <- y[train]
y.test  <- y[test]

grid <- 10^seq(10, -2, length = 100)

ridge_model <- glmnet(x.train, y.train, alpha = 0, lambda = grid)

cv_ridge <- cv.glmnet(x.train, y.train, alpha = 0, lambda = grid)
bestlam <- cv_ridge$lambda.min
bestlam

ridge_pred <- predict(ridge_model, s = bestlam, newx = x.test)

mean((y.test - ridge_pred)^2)

coef(ridge_model, s = bestlam)
```

```{r}

```

```{r}

#Lasso Regression
lasso_model <- glmnet(x.train, y.train, alpha = 1, lambda = grid)

cv_lasso <- cv.glmnet(x.train, y.train, alpha = 1)

bestlam <- cv_lasso$lambda.min
bestlam
```

```{r}
#Predictions + Test MSE
lasso_pred <- predict(lasso_model, s = bestlam, newx = x.test)

mean((y.test - lasso_pred)^2)
```

```{r}
#Coefficients:
predict(lasso_model, type = "coefficients", s = bestlam)
```
Q2

```{r}
############################################################
# 2) Simulation and best subset selection
############################################################

library(leaps)
library(ggplot2)

set.seed(2026)

n <- 100
x <- rnorm(n)
eps <- rnorm(n)
```

```{r}
beta0 <- 1
beta1 <- 2
beta2 <- -3
beta3 <- 1.5

y <- beta0 + beta1*x + beta2*x^2 + beta3*x^3 + eps
```

```{r}
sim.data <- data.frame(
  y = y,
  x1 = x,
  x2 = x^2,
  x3 = x^3,
  x4 = x^4,
  x5 = x^5,
  x6 = x^6,
  x7 = x^7,
  x8 = x^8,
  x9 = x^9,
  x10 = x^10
)

head(sim.data)
```


############################################################

Best subset selection
############################################################
```{r}
regfit <- regsubsets(y ~ ., data = sim.data, nvmax = 10)
reg_summary <- summary(regfit)

reg_summary$cp
reg_summary$bic
reg_summary$adjr2
```
```{r}
which.min(reg_summary$cp)
coef(regfit, which.min(reg_summary$cp))

which.min(reg_summary$bic)
coef(regfit, which.min(reg_summary$bic))

which.max(reg_summary$adjr2)
coef(regfit, which.max(reg_summary$adjr2))

data <- data.frame(CP = reg_summary$cp, numVar = seq(1,10))

ggplot(data, aes(y = CP, x = numVar)) + 
  geom_point(color = "Blue") + 
  geom_line() + 
  theme_bw() +
  scale_x_continuous(breaks = c(1:10), name = "Number of variables")

data <- data.frame(BIC = reg_summary$bic, numVar = seq(1,10))

ggplot(data, aes(y = BIC, x = numVar)) + 
  geom_point(color = "Red") + 
  geom_line() + 
  theme_bw() +
  scale_x_continuous(breaks = c(1:10), name = "Number of variables")

data <- data.frame(adjR2 = reg_summary$adjr2, numVar = seq(1,10))

ggplot(data, aes(y = adjR2, x = numVar)) + 
  geom_point(color = "Dark Green") + 
  geom_line() + 
  theme_bw() +
  scale_x_continuous(breaks = c(1:10), name = "Number of variables")


```

############################################################

Forward selection
############################################################

```{r}
regfit_fwd <- regsubsets(y ~ ., data = sim.data, nvmax = 10, method = "forward")
fwd_summary <- summary(regfit_fwd)

which.min(fwd_summary$cp)
coef(regfit_fwd, which.min(fwd_summary$cp))

which.min(fwd_summary$bic)
coef(regfit_fwd, which.min(fwd_summary$bic))

which.max(fwd_summary$adjr2)
coef(regfit_fwd, which.max(fwd_summary$adjr2))
```


############################################################

Backward selection
############################################################

```{r}
regfit_bwd <- regsubsets(y ~ ., data = sim.data, nvmax = 10, method = "backward")
bwd_summary <- summary(regfit_bwd)

which.min(bwd_summary$cp)
coef(regfit_bwd, which.min(bwd_summary$cp))

which.min(bwd_summary$bic)
coef(regfit_bwd, which.min(bwd_summary$bic))

which.max(bwd_summary$adjr2)
coef(regfit_bwd, which.max(bwd_summary$adjr2))
```

The true model contains $x$, $x^2$, and $x^3$. I used best subset selection, forward selection, and backward selection to choose among models containing $x, x^2, \dots, x^{10}$. I compared the models using $C_p$, BIC, and adjusted $R^2$. The best models should be close to the true cubic model, so I expect the selected predictors to include mainly $x$, $x^2$, and $x^3$.

