---
title: "STT3851 Homework 1"
author: "Dr. Hasthika Rupasinghe"
output: 
    pdf_document: default
    html_document:
      keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Note:** *Submit a printed pdf or an html file. ggplots must be used for all graphics. Graphics created using base commands will not receive credits.* 


1. What are the main two statistical learning types?

2. Find two examples where you can use two types you mentioned in 1) to address the problem. Explain **why** for each example. 


3. Supervised Learning has been broadly classified into 2 types. What are they?



4. Find three examples where you can use **regression**, **classification** and **clustering** to address the problem. Explain **why** for each example. 
 

5. Use the `Auto` data set found in the `ISLR` library to create the scatter plot shown here for `weight` versus `mpg` for each `origin`.
  

  
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(ISLR)
library(ggplot2)
data(Auto)


ggplot(data = Auto, aes(x=weight, y=mpg, color= factor(origin))) + geom_point() + geom_smooth(se=FALSE) + theme_bw()

```


