---
title: "STT3851 Homework 4"
author: "Dr. Hasthika Rupasinghe"
date: Due -- September 22
output: 
    pdf_document: default
    html_document:
      keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1) Provide a sketch of typical (squared) bias, variance, training error, test error, and  irreducible error curves, on a single plot, as we go from less flexible statistical learning methods towards more flexible approaches. The x-axis should represent the amount of flexibility in the method, and the y-axis should represent the values for each curve. There should be five curves. Make sure to label each one.

    b) Explain why each of the five curves has the shape displayed in part (a)
  
  
2) Explain what Bias-Variance trade off is.

3) How can you identify a High Bias model? How can you fix it?  

4) Given the test MSE and the Training MSE, how can you tell if the model suffer from overfitting?

5) We have data from the questionnaires survey (to ask people opinion) and objective testing with two attributes (acid durability and strength)
to classify whether a special paper tissue is good or not. Here is four training samples. Note that $X_1$ = Acid Durability (seconds), $X_2$ = Strength (kg/square meter) and $Y$ = Classification.

```{r echo=FALSE, warning=FALSE, comment=NA, message=FALSE}
library(knitr)
devtools::install_github("lbusett/insert_table")

my_tbl <- tibble::tribble(
  ~X_1, ~X_2, ~Y,
                              "7",                               "7",               "Bad",
                              "7",                               "4",               "Bad",
                              "3",                               "4",              "Good",
                              "1",                               "4",              "Good"
  )

require(rhandsontable)
kable(my_tbl, rowHeaders = NULL,
               digits = 3, useTypes = FALSE, search = FALSE,
               width = NULL, height = NULL)

```


The factory produces a new paper tissue that pass laboratory test with $X_1 = 3$ and $X_2 = 7$. Without another expensive survey, use the following steps to find the classification of this new tissue.

  a) Suppose use $K = 3$
  
  b) Find the euclidean distance between the query-instance (3, 7) and all the training samples. A table might be useful.
  
  c) Rank the distances and figure out which points are included in 3-Nearest neighbors.
  
  d) Use simple majority of the category of nearest neighbors as the prediction value of the query instance. 




