---
title: "STT3851 Homework 6"
author: "Dr. Hasthika Rupasinghe"
date: Due -- October 06
output: 
    pdf_document: default
    html_document:
      keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1) For a simple linear regression model, we are given the following information:

$$\sum_{i=1}^7 (x_i-\bar{x})^2 = 2000,\quad \sum_{i=1}^7 e_i^2 =
967$$

Calculate $SE(\hat{\beta_1})$ the standard error of $\hat{\beta_1}$.

2) Show that the LS estimate, $\hat\beta_1$ can be written as:

$$\hat{\beta}_1 = \frac{\sum_{i=1}^{n} x_iy_i - n\bar{x}\bar{y}}{\sum_{i=1}^{n} x_i^2-n\bar{x}^2}$$

3) Load the `Auto` data set from the `ISLR` library. Consider a simple linear regression model predicting `mpg` using `weight`.

  \begin{enumerate}
    \item Obtain $\sum y_i,\quad \sum x_i, \quad \sum x_i^2,\quad \sum x_iy_i,\quad \sum y_i^2,\quad n$ using R.
    \item Obtain the estimated regression function by finding LS estimates $\hat{\beta_1}$ and $\hat{\beta_0}$ using part 1). 
    \item Plot the estimated regression function and the data.
    \item Does a linear regression function appear to give a good fit here? 
    \item Verify that your fitted regression line goes through the point $(\bar{X}, \bar{Y})$. 
    \item Obtain the residual for the first case. 
    \item Compute $\sum {e_i}^2$ and MSE (You can use R here but do not use the lm function). 
    
\end{enumerate}

```{r include=FALSE}
library(ggplot2)
library(ISLR)
data(Auto)
str(Auto)
ggplot(data = Auto, aes(x=weight, y = mpg)) + geom_point()
```

