---
title: "STT3851 Homework 7"
author: "Dr. Lasanthi Watagoda"
date: Due -- October 12
output: 
    pdf_document: default
    html_document:
      keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the `Carseats` data set from the `ISLR` library. Be sure to explore this data set before answering the questions below. When exploring, the R commands such as `?Carseats`, `str()`, `head()` might be helpful. Consider fitting a simple linear regression to predict the `Sales` using `Age`. 

  \begin{enumerate}
    \item Obtain $\sum y_i,\quad \sum x_i, \quad \sum x_i^2,\quad \sum x_iy_i,\quad \sum y_i^2,\quad n \quad and \quad \sum {e_i}^2$ using R.
    \item Use the following four steps to check whether there is a linear relationship to exist between `Age` and `Sales`.
    
  \begin{enumerate}
  \item State the null and alternative hypothesis:
  \item Calculate the t test statistic using the quantities you computed above (Hint: First find $\hat{\beta_1}$ and MSE. Secondly find $SE({\hat{\beta_1}})$)
  \item Find the $p$-value using R. (I did not provide a command to do this in class.)
  \item Make the decision:
    \end{enumerate}
    
  \item Use the `lm()` function along with the `summary()` function to repeat the 4-step hypothesis test above
  \begin{enumerate}
  \item State the null and alternative hypothesis
  \item Get the t test statistic from the output
  \item Get the $p$-value from the output
  \item Make the decision
    \end{enumerate}
    
\end{enumerate}

```{r include=FALSE}
library(ISLR)
data("Carseats")
head(Carseats)
library(ggplot2)
ggplot(data = Carseats, aes(x=Age, y = Sales)) + geom_point()
```


