---
title: "STT3851 Homework 7"
author: "Dr. Hasthika Rupasinghe"
date: Due -- October ??
output: 
    pdf_document: default
    html_document:
      keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the `Carseats` data set from the `ISLR` library. Be sure to explore this data set before answering the questions below. When exploring, the R commands such as `?Carseats`, `str()`, `head()` might be helpful. 

  \begin{enumerate}
    \item Fit a linear regression to predict the `Sales` using `Age` and `Income`. 
    \item Conduct a hypothesis test to check if there is a relationship between `Sales` and the predictor variables `Age` and `Income`.
    
  \begin{enumerate}
  \item Null and alternative hypothesis:
  \item Test statistic 
  \item $p$-value
  \item Make the decision:
    \end{enumerate}
    
  \item Fit a linear regression to predict the `Sales` using `Age`,  `Income` and the interaction between `Age` and the  `Income`.
  
  \item Conduct a hypothesis test to check if the interaction term is useful in the model above
  
  \begin{enumerate}
  \item Null and alternative hypothesis:
  \item Test statistic 
  \item $p$-value
  \item Make the decision:
    \end{enumerate}
    
\end{enumerate}

```{r include=FALSE}
library(ISLR)
data("Carseats")
head(Carseats)
library(ggplot2)
ggplot(data = Carseats, aes(x=Age, y = Sales)) + geom_point()
m <- lm(Sales ~ Age + Income, data = Carseats)
summary(m)

m <- lm(Sales ~ Age + Income + Age*Income, data = Carseats)
```


