---
title: "Writing Assignment"
author: "Leave This Blank"
bibliography: [packages.bib, ISLR.bib]
output: 
    bookdown::html_document2
date: 'Last compiled: `r format(Sys.time(), "%b %d, %Y")`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,comment = NA)
```

## Directions{-}
Recreate this document exactly using [R Markdown](https://rmarkdown.rstudio.com/). A great reference for creating technical documents with R Markdown is [bookdown: Authoring Books and technical withR Markdown](https://bookdown.org/yihui/bookdown/). Your YAML should look similar to:

```{r, eval=FALSE}
---
title: "Writing Assignment"
author: "Leave This Blank"
bibliography: [packages.bib, ISLR.bib]
output: 
    bookdown::html_document2
date: 'Last compiled: `r format(Sys.time(), "%b %d, %Y")`'
---
```

# From page 62 of [ISLR](http://www-bcf.usc.edu/~gareth/ISL/ISLR%20Sixth%20Printing.pdf) [@james_introduction_2013]
let $\hat y_i = \hat \beta_0 + \hat \beta_1 x_i$ be the prediction for $Y$ based on the $i^{\text{th}}$ value of $X$. Then $e_i=y_i+\hat y_i$ represents the $i^{\text{th}}$ *residual*---this is the difference between the $i^{\text{th}}$ observed response and the $i^{\text{th}}$ response value that is predicted by our linear model. We define the **residual sum of squares** (RSS) as
\begin{equation}
\mathrm{RSS} = e^2_1 + e^2_2 + ... + e^2_n.
\end{equation}

or equivalently as 

\begin{equation}
\mathrm{RSS}=(y_1-\hat \beta_0 - \hat \beta_1 x_i)^2+(y_2- \hat \beta_0 + \hat \beta_1 x_2)^2+...+(y_n - \hat \beta_0 + \hat \beta_1 x_n)^2
(\#eq:RSS)
\end{equation}

The least squares approach chooses $\hat \beta_0$ and $\hat \beta_1$ to minimize the RSS. Using some calculus,one can show that the minimizers are 

\begin{equation}
\begin{split}
\hat \beta_1 = \frac{\sum^n_{i=1}(x_i-\bar x)(y_i- \bar y)}{\sum^n_{i=1}(x_i-\bar x)^2} ,\\
\hat \beta_0 = \bar y - \hat \beta_1 \bar x,\\
\end{split}
(\#eq:b1b0)
\end{equation}

where $\bar y \equiv \frac{1}{n}\sum^n_{i=1}y_i$ and $\bar x \equiv \frac{1}{n}\sum^n_{i=1}x_i$ are the sample means.


# From Page 63 of [ISLR](http://www-bcf.usc.edu/~gareth/ISL/ISLR%20Sixth%20Printing.pdf)[@james_introduction_2013]

Recall that we assume that the true relationship between $X$ and $Y$ takes the form $Y=f(X)+\epsilon$ for some unknown function $f$, where $ϵ$ is a mean-zero random error term. If $f$ is to be approximated by a linear function, then we write this relationship as

\begin{equation}
\mathrm{Y}= \beta_0 + \beta_1 + \epsilon,\\
(\#eq:Y)
\end{equation}

Here $\beta_0$ is the intercept term---that is, the expected values of  $Y$ when $X=0$, and $\beta_1$ is the slope--- thw average increase in $Y$ associated with one-unit increase in $X$. The error term is a catch-all for what we miss with this simple model: the true relationship is probably not linear, there may be other variables that cause variation in $Y$, and there may be measurment error. We typically assume that the error term is independent of $X$.

# From page 143 of [ISLR](http://www-bcf.usc.edu/~gareth/ISL/ISLR%20Sixth%20Printing.pdf) [@james_introduction_2013]

To indicate that a $p-dimensional$ random variable $X$ has a multivariate Gaussian distribution, we write $X$ ~ $N(\mu,\sum)$. Here $E(X) = \mu$ is the mean of $X$ (a vector with p components), and $Cov(X)= \sum$  is the p x p covariance matrix of $X$. Formally, the multivariate Gaussian density is defined as

\begin{equation}
\mathrm{f(x)} = \frac{1}{2\pi}^{p/2} \sum exp(\frac{1}{2}(x-\mu)^T \sum^{-1}(x-\mu
(\#eq:1)
\end{equation}

In the case of p>1 predictors, the LDA classifier assumes that the observatons in the k^th^ class are drawn from a multivariate Gaussian distribution $N(\mu_\kappa, \sum)$, where $\mu_\kappa$ is a class-specific mean vector, and $\sum$ is the covariance matrix that is common to all $K$ classes. Plugging the density function for the k^th^ class, $f_k(X=x)$, into ([3.1](https://lasanthi-asu.github.io/STT3851ClassRepo/Rmarkdown/WritingAssignment.html#eq:mgd)) and performing a little bit of algebra reveals that the Bayes classifier assigns an observation $X=x$ to the class for which

\begin{equation}
\mathrm{\delta_\kappa(x)}= x^T \sum^{-1} \mu_\kappa - \frac{1}{2}\mu^T_\kappa\sum^{-1}\mu_\kappa + log\pi_\kappa
(\#eq:2)
\end{equation}

is the largest






# Inserting a graph

```{r, label= "hist", fig.align='center', fig.cap= "Your descriptive caption here"}
set.seed(123)
x <- rnorm(1000, 100, 15)
DF <- data.frame(x = x)
library(ggplot2)
ggplot(data = DF, aes(x = x)) + 
  geom_histogram(fill = "blue", color = "black", binwidth = 5) + 
  theme_bw()

xbar <- mean(x)
SD <- sd(x)
c(xbar, SD)
```

figure \@ref(fig:hist) is unimodal with amean of `r round(mean(x),4)` and a stendard deviation of `r round(sd(x),4)`

#Automagically Creating References

```{r, echo=FALSE, results='hide'}
packagesUsed <- c("ggplot2", "bookdown")
#write bib information
knitr::write_bib(packagesUsed, file = "./packages.bib")
#Load packages
lapply(packagesUsed, library, character.only = TRUE)
```

Review your last assignment to create a file named `packages.bib` to cite the `ggplot2` package used to create Figure \@ref(fig:hist). Figure \@ref(fig:hist) was created with `ggplot2` by Wickham and Chang (2016). This document specifies the output as `bookdown::html_document2`. The function  `bookdown::html_document2` is from `bookdown` written by Xie (2016).

```{r}
sessionInfo()
```


written by @-bookdown