---
title: "R Markdown Basics"
author: "Lasanthi"
date: "1/17/2018"
output: html_document
---

### Code Chunks

```{r chunk_name}
#table(cars) 
head(cars)
summary(cars)
```

Note: Click on the `play` button to run the code chunk.

### Chunk Options

To hide your code chunk from the output use `echo=FALSE`.


Note: ERROR
Change the chunk_name

```{r no_code, echo=FALSE}
hist(cars$speed, xlab = "speed", main = "Histogram of Speed")
?hist


```

You use `results="hide"` to hide the results/output (but here the code would still be displayed).

```{r no_output, results="hide"}
cor(cars$speed,cars$dist)
```


You use `include=FALSE` to have the chunk evaluated, but neither the code nor its output displayed.

```{r no_output_no_code, include=FALSE}
cor(cars$speed,cars$dist)
```


### Figures

For figures, you’ll want to use options like fig.width and fig.height. For example:

```{r scatterplot, fig.width=6, fig.height=4, fig.align='center'}
plot(cars$speed,cars$dist)
?plot
```

Note: Change the height and width of the plot.

### In-line code

Here is an example of an in-line code.

There are `r nrow(cars)` cars in the `cars` dataset.
The highest speed recorded was `r max(cars)`.
The correlation between the `speed` and the `distane` is `r cor(cars$speed, cars$dist)`

Convet this html file to a pdf
Inclde the system date 
date: "`r Sys.Date()`"

Change



