---
title: "R Markdown Basics"
author: "Lasanthi"
date: "`r Sys.Date()`"
output: pdf_document
---

##Code Chunks
```{r chunk_name}
#table(cars)
head(cars)
summary(cars)
```


Note: Click on the `play`button to run the code chunk.


###Chunk Options

To hide your code chunk from the output use `echo=FALSE`
```{r no_code, echo = FALSE, fig.align='center'}
hist(cars$speed, xlab = "speed", main = "Histogram of speed" )
?hist

```


You use `results = "hide"` to hide the results/output (but here the code would still be displayed)


```{r no_ouput,results = "hide"}
cor(cars$speed, cars$dist)
?cor
```

You use `include = FALSE` to have the chunk evaluated, but neither the code nor its output displayed.

```{r no_output_no_code, include = FALSE}
cor(cars$speed, cars$dist)
```

###Figures


For figures, you"ll want to use options like fig.width and fig.height. For example

```{r scatterplot, fig.width=6, fig.height= 4, fig.align= "left"}

plot(cars$speed, cars$dist)

```
Note: Change the height and the width of the plot.

###In-line code

Here is an example of an in-line code

There are `r nrow(cars)` cars in the `cars`dataset.


