---
title: "Bootstarp Example"
author: ""
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  bookdown::html_document2: 
    highlight: textmate
    theme: yeti
---

```{r, label = "SETUP", echo = FALSE, results= 'hide', message = FALSE, warning = FALSE}

```

**Estimating the Accuracy of a Linear Regression Model**


First step is to define your `bootstarap function` according to the problem.
Here I am using the `Auto` data set to fit a `linear regression`.
```{r}
library(ISLR)
attach(Auto)
Auto
```


```{r}
bootfun =function(mydata, index)
{
    lmfit <- lm(mpg~horsepower, data = mydata, subset =index)
    coeffients <- coef(lmfit)
    return(coeffients)
  
}
```


Now we can use the funtion defined above to find the original estimates for the slope and intercept

```{r}
bootfun(Auto, 1:392)

```

We haven't still done any `bootstarps`. But we can use our function to do the bootstrap.
All we have to do is, instead of `1:392`, use a `random sample`. 


```{r}
sample(1:392, 392, replace = TRUE)
bootfun(Auto, sample(1:392, 392, replace = TRUE))

```


```{r}
bootfun(Auto, sample(1:392, 392, replace = TRUE))

```

```{r}
bootfun(Auto, sample(1:392, 392, replace = TRUE))

```

```{r}
bootfun(Auto, sample(1:392, 392, replace = TRUE))

```

We use the `boot()` funtion in the **boot** `library` to compute as many bootstrap samples as we want.



```{r}
library(boot)

boot(Auto, bootfun, 1000)
```



```{r}
lmfit <- lm(mpg~horsepower, data = Auto)
summary(lmfit)$coef
```

**Chapter 5 Exercise 9**

Let's conside the `Boston` housing dataset from the `MASS` library.

```{r}
library(MASS)
set.seed(203)
attach(Boston)
summary(Boston)
```


a) Based on this data set, provide an estimate for the population
mean of `medv`. Call this estimate $\hat\mu$.

```{r}
mean_medv <- mean(medv)
mean_medv
```

b) Provide an estimate of the standard error of $\hat\mu$. Interpret this
result.

*Hint: We can compute the standard error of the sample mean by
dividing the sample standard deviation by the square root of the
number of observations.*

```{r}
SE_medv <- sd(medv)/sqrt(length(medv))
SE_medv
```


c) Now estimate the standard error of $\hat\mu$ using the bootstrap. How
does this compare to your answer from (b)?

First define our function to find the mean of `medv`

```{r}
bootfun <- function(mydata, index) 
{
  mean_medv_bootstrap <- mean(mydata[index])
  return(mean_medv_bootstrap)
}

library(boot)

bootstrap_mean <- boot(medv, bootfun, 1000)
bootstrap_mean
```

In this situation, answer(SE) from b) and c) are similar. (But, it could be different too.)

d) Based on your bootstrap estimate from (c), provide a 95% confidence
interval for the mean of medv. Compare it to the results obtained using `t.test(medv)`.

*Hint: You can approximate a 95 % confidence interval using the
formula $[\hat\mu − 2SE(\hat\mu), \hat\mu + 2SE(\hat\mu)]$*

**CI from bootstrap:** 

```{r}
c(22.53281 - 2*0.4085688, 22.53281 + 2*0.4085688)
```


**CI from `t.test`:** 

```{r}
t.test(medv)
```

e) Based on this data set, provide an estimate, $\hat\mu_med$, for the median
value of `medv` in the population.


```{r}
median_medv <- median(medv)
median_medv
```


f) We now would like to estimate the standard error of $\hat\mu_med$. Unfortunately,
there is no simple formula for computing the standard error of the median. Instead, estimate the standard error of the median using the bootstrap. Comment on your findings.

First define our function to find the median of `medv`

```{r}
bootfun2 <- function(mydata, index) 
{
  median_medv_bootstrap <- median(mydata[index])
  return(median_medv_bootstrap)
}

library(boot)

bootstrap_median <- boot(medv, bootfun2, 1000)
bootstrap_median
```

`medv` has a median of 21.2 with and SE of 0.3797466


g) Based on this data set, provide an estimate for the tenth percentile
of `medv` in Boston suburbs. Call this quantity $\hat\mu_{0.1}$. (You
can use the `quantile()` function.)

```{r}
tenth_percentile_medv <- quantile(medv, c(0.1))
tenth_percentile_medv
```

h) Use the bootstrap to estimate the standard error of $\hat\mu_{0.1}$. Comment
on your findings.

```{r}
bootfun3 <- function(mydata, index) 
{
  tenth_percentile_medv_boot <- quantile(mydata[index], c(0.1))
  return(tenth_percentile_medv_boot)
}

library(boot)

bootstrap_tenth_percentile_med <- boot(medv, bootfun3, 1000)
bootstrap_tenth_percentile_med
```


